\documentclass[12pt,a4paper,oneside]{report}


\usepackage{amsmath,amssymb,calc,ifthen}

\usepackage{float}
%\usepackage{cancel}

\usepackage[table,usenames,dvipsnames]{xcolor} % for coloured cells in tables

\usepackage{tikz}

\usepackage{mathptmx}

\usepackage{hyperref}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=black,
    urlcolor=black
}

% Nice package for plotting graphs
% See excellent guide:
% http://www.tug.org/TUGboat/tb31-1/tb97wright-pgfplots.pdf
\usetikzlibrary{plotmarks}
\usepackage{amsmath,graphicx}
\usepackage{epstopdf}
\usepackage{caption}
\usepackage{subcaption}

% highlight - useful for TODOs and similar
\usepackage{color}
\newcommand{\hilight}[1]{\colorbox{yellow}{#1}}

\newcommand\ci{\perp\!\!\!\perp} % perpendicular sign
\newcommand*\rfrac[2]{{}^{#1}\!/_{#2}} % diagonal fraction

\usepackage{listings}



% margin size
\usepackage[margin=2cm]{geometry}

\tikzstyle{state}=[circle,thick,draw=black, align=center, minimum size=2.1cm,
inner sep=0]
\tikzstyle{vertex}=[circle,thick,draw=black]
\tikzstyle{terminal}=[rectangle,thick,draw=black]
\tikzstyle{edge} = [draw,thick]
\tikzstyle{lo} = [edge,dotted]
\tikzstyle{hi} = [edge]
\tikzstyle{trans} = [edge,->]


\begin{document}
\belowdisplayskip=12pt plus 3pt minus 9pt
\belowdisplayshortskip=7pt plus 3pt minus 4pt


\section*{MiniMD Summary}

% The first week was focused on Neuroimaging and was based at Queen Square. We attended many multidisciplinary team meetings (MDTs) where neurologists, radiologists and other doctors were discussion unusual or difficult patient cases. 

\section*{Positive aspects} 

I liked the interactive or practical sessions such as the vascular surgeries in RFH, dementia and diabetes clinics. I also particularly liked the microvascular laboratory. 

\section*{Negative aspects}

I enjoyed less the neurology MDTs as they were not as interactive as we expected and for the fact that we got lost very easily in the discussion. 

\section*{Suggestions for improvement}

1. It would be great to have one registrar or even research fellow as our buddy, going around with us and explaining what is going on, mostly for the MDTs or got the Gowers (where registrars are assessed by a consultant). The buddy system would also be great as we could discuss research ideas.  \\
2. It would've also been very nice to have a more general focus on Neuro in the first week, as opposed to Neuroimaging. More precisely, as I work with cognitive tests, it would've been great to also attend neuropsychological assessments (MMSE, ADAS-COG, RAVLT, etc ...). \\
3. More dementia clinics like the MS clinic (on typical and atypical AD, FTDs, KJD) and less MDTs.
4. More laboratories like the microvascular lab.

\section*{The value to you of participating}

As I work with dementia, the first week in Neuroimaging was very valuable for me. I found out that diffusion imaging is actally used in clinical practice, for diagnosis of tumors and even tuberculosis (if I remember correctly). Moreover, I could observe how doctors and radiologists take decisions about treatments or surgical interventions. 

\end{document}
